---
title: "R final"
output: html_document
date: "2022-12-11"
---

# Specify the file path

file_path \<- "C:/Users/Shweta/Downloads/Electric Vehicle Population Data (1).csv"

# Read the CSV file into a data frame

Electric_Vehicle_Population_Data \<- read.csv(file_path)

# Display the first few rows of the data frame to confirm it was read correctly

head(Electric_Vehicle_Population_Data)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(dplyr)
```

```{r}
is.null(Electric_Vehicle_Population_Data)
```

## Dataset cleaning for NULL values

```{r}
Electric_Vehicle_Population_Data %>%
  select(VIN, County, City, State, ZIP_Code, Model_Year, Make, Model, Electric_Vehicle_Type, CAFV, Range_Km, Base_MSRP, Legislative_District, DOLVehicleID, VehicleLocation, ElectricUtility) %>% na.omit()
```

```{r}
table(Electric_Vehicle_Population_Data["City"])
```

```{r}
table(Electric_Vehicle_Population_Data["Make"])
```

## Comparision between city vs Car Company(Make)

```{r}
NEW_TABLE <- Electric_Vehicle_Population_Data %>% count(City , Make , sort = TRUE)
NEW_TABLE
```

## \## Comparision between city vs Year of manufacture

```{r}
NEW_TABLE <- Electric_Vehicle_Population_Data %>% count(City , Model_Year , sort = TRUE)
NEW_TABLE
```

## Comparision between city vs Electric vehicle type( plug-in / hybrid)

```{r}
NEW_TABLE <- Electric_Vehicle_Population_Data %>% count(City , Electric_Vehicle_Type , sort = TRUE)
NEW_TABLE
```

```{r}
NEW_TABLE <- Electric_Vehicle_Population_Data %>% count(City , Model , sort = TRUE)
NEW_TABLE
```
## TO SHOW THE PREFERENCE OF ELECTRIC VEHICLE TYPE {BEV/PHEV) IN CITIES AND TAKING THE TOP 20 COUNT.

##```{r} 
##NEW_TABLE %>% 
##   slice(1:20) %>% 
##ggplot(., aes( x= city, y = n, color = Electric_vehicle_Type)) + 
##  geom_bar (stat = 'identity') + 
##labs (title ="ELECTRIC VEHICLE TYPE PER CITY") + 
##  theme (axis.text.x=element_text (angle = -90, hjust = 0))
##```

## TO SHOW THE PREFERENCE OF ELECTRIC VEHICLE TYPE (BEV/PHEV) IN CITIES AND TAKING THE TOP 20 COUNT.

# Create the new table with counts

```{r}
NEW_TABLE <- Electric_Vehicle_Population_Data %>% 
  count(City, Electric_Vehicle_Type, sort = TRUE)
```

# Filter to get the top 20 counts

```{r}
top_20 <- NEW_TABLE %>% 
  slice(1:20)
```

# Plot using ggplot2

```{r}
ggplot(top_20, aes(x = City, y = n, fill = Electric_Vehicle_Type)) + 
  geom_bar(stat = "identity") + 
  labs(title = "ELECTRIC VEHICLE TYPE PER CITY") + 
  theme(axis.text.x = element_text(angle = -90, hjust = 0))
```

# Create the new table with counts

```{r}
NEW_TABLE3 <- Electric_Vehicle_Population_Data %>% 
  count(Make, Model_Year, Electric_Vehicle_Type, sort = TRUE)
```

# Plot using ggplot2
```{r}
ggplot(data = NEW_TABLE3, mapping = aes(x = Make, y = Model_Year, size = n, color = Electric_Vehicle_Type)) + 
  geom_point() +
  labs(title = "Electric Vehicles Type Increase per Brand with Respect to Year") +
  theme(axis.text.x = element_text(angle = -90, hjust = 0))
```
# Create the new table with counts or summary statistics

```{r}
NEW_TABLE2 <- Electric_Vehicle_Population_Data %>% 
  group_by(State, Electric_Vehicle_Type, Make, Model_Year) %>%
  summarise(count = n(), .groups = 'drop')
```

# Plot using ggplot2

```{r}
ggplot (NEW_TABLE, aes(Electric_Vehicle_Type, State, color = Make, size = Year)) + 
  geom_boxplot (size = 1) +
  labs(title = "Statewise increase in Electric vehicles Type with respect to Brand " )

```
# Create the new table with counts or summary statistics

```{r}
NEW_TABLE2 <- Electric_Vehicle_Population_Data %>% 
  group_by(State, Electric_Vehicle_Type, Make, Model_Year) %>%
  summarise(count = n(), .groups = 'drop')
```

# Plot using ggplot2

```{r}
ggplot (NEW_TABLE2, aes(Electric_Vehicle_Type, State, color = Make, size = Year)) + 
  geom_boxplot(size = 1) +
  labs(title = "Statewise increase in Electric vehicles Type with respect to Brand ")
```

# Create NEW_TABLE4 by counting occurrences of Make in each city per year

```{r}
NEW_TABLE4 <- Electric_Vehicle_Population_Data %>%
  group_by(city, Model_Year, Make) %>%
  summarise(n = n(), .groups = 'drop') %>%
  arrange(desc(n))
```

```{r}
NEW_TABLE4 <- NEW_TABLE4 %>%
  group_by(Model_Year) %>%
  top_n(40, n)
```


## TO SHOW TOP PREFERED ELECTRIC VEHICLE MANUFACTURING MAKE (BRANDS} IN TOP 40 CITIE PER YEAR. 
```{r}
NEW_TABLE4 %>% 
 slice(1:40) %>%
ggplot (. , mapping = aes (x = city, y = n, color = Make)) + 
geom_point + 
facet_wrap (~ Model_Year) +
 labs (title = "Top Electric Vehicle Manufacturing Companies From 2013 to 2022" ) + 
  theme (axis.text.x=element_text (angle = -90, hjust = 0))
```
# Create NEW_TABLE4 by counting occurrences of Make in each city per year
  # Arrange by descending count to get top preferences
```{r}
NEW_TABLE4 <- Electric_Vehicle_Population_Data %>%
  group_by(City, Model_Year, Make) %>%
  summarise(n = n(), .groups = 'drop') %>%
  arrange(desc(n))
```

# Filter to get the top 40 cities per year

```{r}
NEW_TABLE4 <- NEW_TABLE4 %>%
  group_by(Model_Year) %>%
  top_n(40, n)
```

# Plot using ggplot2

```{r}
ggplot(NEW_TABLE4, aes(x = City, y = n, color = Make)) + 
  geom_point() + 
  facet_wrap(~ Model_Year) +
  labs(title = "Top Electric Vehicle Manufacturing Companies From 2013 to 2022") + 
  theme(axis.text.x = element_text(angle = -90, hjust = 0))
```



